Brownian Dynein Model

### 2015-10-29 latex/derivation.tex
quick commitgit add latex/derivation.tex

\newcommand{\shellcmd}[1]{\texttt{\footnotesize #1}}

@@

We want to find cartesian coordinates in terms of $L_n$ and $L_f$.\\

Also by the law of cosines, we see that:
\begin{align}
  \Theta_{1} &= \cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg) \\
  \Theta_{2} &= \pm\cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg) \\
\end{align}

We use these equations to solve for our nm (near motor) coordinates:

@@

\begin{align}
  \dot{X}_{nm} =
  &-\frac{\text{Ls} \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4
   \text{Ls}^2 \text{Ln}(t)^2}} \left(\frac{\text{Ln}'(t)
   \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{2 L^2
   \text{Ln}(t)^3}-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right) \left(2
   \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t) \text{Lf}'(t)\right)}{2 L^2
   \text{Ln}(t)^2}\right)}{2
   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2
   \text{Ln}(t)^2}}} - \\
  &\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)
   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{2 L \text{Ls}
   \text{Ln}(t)^3}\\
  &-\frac{\text{Ls}
   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2 \text{Ln}(t)^2}}
   \left(\frac{\text{Ln}'(t) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{2
   \text{Ls}^2 \text{Ln}(t)^3}-\frac{\text{Ln}'(t)
   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{\text{Ls}^2 \text{Ln}(t)}\right)}{2
   \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4 \text{Ls}^2
       \text{Ln}(t)^2}}}\\
  & +\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)}{2
   L \text{Ls} \text{Ln}(t)}+\frac{\left(2 \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t)
   \text{Lf}'(t)\right) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{4 L \text{Ls}
   \text{Ln}(t)^2}
\end{align}

We can also use the law of cosines to find an expression for $\Theta_{1}$:

\begin{align}
   L_f^2 &= L^2 + L_n^2 - 2LL_n\cos(\Theta_{1}) \\
   \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
\end{align}

We use this to find the value of $X_{t}$:

@@

To find $Y_{t}$ we do something similar:

\begin{align}
  \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
  Y_{t} &= L_n\sin(\Theta_{1}) \\
  &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
\end{align}

>>>>

\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins

@@

By the law of cosines, we see that:
\begin{align}
  \Theta_{1} &= \cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg) \\
  \Theta_{2} &= \pm\cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg) \\
\end{align}

\subsection{Solving for $X_{nm}$ and $Y_{nm}$}

@@

\begin{align}
  \dot{X}_{nm} &=\\
\end{align}

\subsection{$X_t$ and $Y_t$}

@@

\begin{align}
  Y_{t} &= L_n\sin(\Theta_{1}) \\
  &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
\end{align}
